---
title: "knugo Test File"
---

# knugo Test File

This document serves as a test case for the **knugo** package, demonstrating
how various output types are rendered for a Hugo-centric workflow.

## 1. HTML Widget Example

Below is an example using an HTML widget (e.g., from the **DT** package).g

```{r htmlwidget-example, echo=FALSE}
# Load DT package (make sure it's in your package dependencies)
library(DT)
# Create a simple interactive data table
datatable(iris)
```

## 2. Table Example with kable

Here we generate a table using `knitr::kable()` to display the first few rows
of the `mtcars` dataset.

```{r kable-table, echo=TRUE}
library(knitr)
# Create a table with a caption
kable(head(mtcars), caption = "Table: First 6 rows of mtcars")
```

## 3. ggplot2 Plot Example using svglite

This chunk creates a **ggplot2** plot rendered with **svglite**. The plot is
produced as an SVG image.

```{r ggplot-svglite, fig.width=6, fig.height=4, echo=TRUE}
library(ggplot2)
# Create a scatter plot of mpg vs weight
p <- ggplot(mtcars, aes(x = wt, y = mpg)) +
  geom_point() +
  ggtitle("Scatterplot of mpg vs. weight")
print(p)
```

## 4. Code Example

A simple R code chunk that computes the sum of the first 10 natural numbers.

```{r code-demo, echo=TRUE}
# Calculate the sum of numbers 1 through 10
result <- sum(1:10)
result
```

## 5. Inline Code Example

You can also include inline R code. For instance, the sum of 1 through 10 is
`r sum(1:10)`.

```
